Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-08-28 paper/ms.tex
update submit date
update manuscript with amended f11

\documentclass[12pt,twocolumn,tighten]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{TOI~837 in IC~2602}

@@

Finding and understanding systems undergoing these evolutionary changes is
a major goal in contemporary exoplanet research.  To identify stars
younger than say 1$\,$Gyr, a number of direct and indirect methods are
available \citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified isochronally, provided that
they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
age indicators include stellar rotation periods, the abundance of
photospheric lithium, and chromospheric diagnostics such as calcium
emission and broadband UV emission.  Studies by, for instance,
\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
have combined these methods to age-date individual field stars hosting
transiting planets.  Many of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by, {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~2523, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported orbiting
V830~Tau\footnote{Follow-up by Damasso et al{.} (2020, submitted) did
not confirm the planetary signal in V830~Tau.}, TAP~26, and CI~Tau
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.

@@

The TESS Science Processing Operations Center
\citep{jenkins_tess_2016} processed the image data and identified the
transiting planet signature from two transits in
Sector 10, again with three transits in Sector 11, and then for a
final time when Sectors 1--13 were searched at the end of the first
year of the mission. The transit signature was fitted with a
limb-darkened transit model \citep{li_kepler_2019} and passed all the
diagnostic tests \citep{twicken_kepler_2018}, including the odd/even
depth test, the weak secondary eclipse test, the ghost diagnostic
test, and the difference image centroiding test, which placed the
transit source within $\sim$2 arcsec of the location of TOI~837. No
additional transit-like features were identified in any of the SPOC
searches. The TESS Science Office alerted the community to this
candidate transiting planet on 17 June 2019.  Our subsequent blind
search of the CDIPS FFI light curves also showed the transits. Given
that the 2-minute data had better sampling cadence, we opted to use
the Presearch Data Conditioning (PDC) light curve with the default
aperture for our
analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,smith_finding_2016}.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Planet radii versus ages, for the known transiting planets.} 
    Systems younger than 100$\,$Myr are emphasized.  Ages and radii
    are from the NASA Exoplanet Archive on 29 July 2020.  Precise ages
    are known for only a small fraction of the gray points.
		\label{fig:rpvsage}
	}
	\vspace{-0.2cm}
\end{figure}

\tn\ joins a number of other young planetary systems reported from
TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
\citep{newton_tess_2019,zhou_well_2020,montet_young_2020,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
Figure~\ref{fig:rpvsage} shows \tn\ in the space of planet sizes and
ages.  \tn\ is among the youngest transiting planets known.

@@

If the RM measurements prove that the validated planet is real,
measuring its mass may be worth the effort, because it would improve
understanding of the planet's contraction and photoevaporation.  If an
RV campaign were timed to coincide with TESS Sectors 36 and 37 (3
March 2021 through 28 April 2021), it would significantly ease
extraction of the Keplerian signal.  The reason is that the RVs,
activity indicators, and photometry could be modeled simultaneously
\citep[{\it e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.
Combining photometric and radial velocity data from non-overlapping
epochs would also constrain the models, but perhaps not quite as
convincingly.

@@

\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{ceres} \citep{brahm_2017_ceres},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano},
	\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  \texttt{IPython} \citep{perez_2007},
	\texttt{isochrones} \citep{morton_2015_isochrones},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  \texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
	\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  \texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
\

>>>>

%\documentclass[12pt,twocolumn,tighten]{aastex63}
\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{August 6, 2020}
\revised{---}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{TOI~837 in IC~2602}

@@

Finding and understanding systems undergoing these evolutionary changes is
a major goal in contemporary exoplanet research.  To identify stars
younger than say 1$\,$\replaced{Gyr}{gigayear}, a number of direct and indirect methods are
available \citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified isochronally, provided that
they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
age indicators include stellar rotation periods, the abundance of
photospheric lithium, and chromospheric diagnostics such as calcium
emission and broadband UV emission.  Studies by, for instance,
\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
have combined these methods to age-date individual field stars hosting
transiting planets.  Many of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by, {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

\explain{NOTE: removed footnote to Damasso et al 2020 in prep, since
it has now been published, and added note to Donati et al 2020.}
A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~\replaced{2523}{2423}, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported orbiting V830~Tau, TAP~26,
and CI~Tau
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
\added{
The planetary nature of at least two of these signals has been debated
\citep{donati_magnetic_2020,damasso_gaps_2020}.
}

@@

The TESS Science Processing Operations Center
\citep{jenkins_tess_2016} processed the image data and identified the
transiting planet signature from two transits in
Sector 10, again with three transits in Sector 11, and then for a
final time when Sectors 1--13 were searched at the end of the first
year of the mission. The transit signature was fitted with a
limb-darkened transit model \citep{li_kepler_2019} and passed all the
diagnostic tests \citep{twicken_kepler_2018}, including the odd/even
depth test, the weak secondary eclipse test, \deleted{the ghost diagnostic
test,} and the difference image centroiding test, which placed the
transit source within $\sim$2 arcsec of the location of TOI~837. No
additional transit-like features were identified in any of the SPOC
searches. The TESS Science Office alerted the community to this
candidate transiting planet on 17 June 2019.  Our subsequent blind
search of the CDIPS FFI light curves also showed the transits\added{,
as did that of \citet{nardiello_pathosII_2020}}. Given
that the 2-minute data had better sampling cadence, we opted to use
the Presearch Data Conditioning (PDC) light curve with the default
aperture for our
analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,smith_finding_2016}.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f11a.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f11b.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    \explain{The bottom sub-panel of this figure has been added
    in revision.}
    {\bf \tn\ compared to known transiting planets}.
    {\it Top}: Planet radii versus ages.  Systems younger than
    100$\,$Myr are emphasized.  Ages and radii are from the NASA
    Exoplanet Archive on 27 Aug 2020.  Precise ages are known for only
    a small fraction of the gray points.
    {\it Bottom}: Planet radii versus orbital periods. The known young
    transiting planets do not obviously overlap with the populations of
    known hot Jupiters or sub-Neptunes.
		\label{fig:population}
	}
	\vspace{-0.2cm}
\end{figure}

\tn\ joins a number of other young planetary systems reported from
TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
\citep{newton_tess_2019,zhou_well_2020,montet_young_2020,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
\replaced{ Figure~\ref{fig:rpvsage} shows \tn\ in the space of planet
sizes and ages.  \tn\ is among the youngest transiting planets known.
}{ In the space of planet sizes and ages, the top panel of
Figure~\ref{fig:population} shows that \tn\ is among the youngest
transiting planets known.  }

\added{In the space of planet sizes and orbital periods, the bottom
panel of Figure~\ref{fig:population} highlights a peculiar feature of
the known sub-100$\,$Myr transiting planets: they do not overlap with
the known populations of either hot Jupiters or sub-Neptune sized
planets.  The young planets instead have sizes ranging from
4.2$\,R_\oplus$ (AU Mic b) to slightly smaller than Jupiter.  The lack
of sub-Neptune sized planets could be a selection effect, because
larger planets are easier to detect around highly variable stars.
Another (speculative) explanation is that the known
sub-100$\,$Myr planets are currently enveloped by primordial H/He
atmospheres, and that they will become sub-Neptune sized planets after
undergoing atmospheric escape \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,gupta_sculpting_2019,gupta_signatures_2020}.
}

@@

If the RM measurements prove that the validated planet is real,
measuring its mass may be worth the effort, because it would improve
understanding of the planet's \replaced{contraction and
photoevaporation}{composition and therefore future atmospheric
evolution}.  If an RV campaign were timed to coincide with TESS
Sectors 36 and 37 (3 March 2021 through 28 April 2021), it would
significantly ease extraction of the Keplerian signal.  The reason is
that the RVs, activity indicators, and photometry could be modeled
simultaneously \citep[{\it
e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.  Combining
photometric and radial velocity data from non-overlapping epochs would
also constrain the models, but perhaps not quite as convincingly.

@@

\software{
  \texttt{arviz} \citep{arviz_2019},
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{ceres} \citep{brahm_2017_ceres},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano},
	\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  \texttt{IPython} \citep{perez_2007},
	\texttt{isochrones} \citep{morton_2015_isochrones},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  \texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
	\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  \texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
\
